---
title: "Hate Crime Visualization"
author: "The authors"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
pkgs2use<- c('flexdashboard','tidyverse','maps','DT','zoo','here','lubridate','tsibble','feasts','fable','hrbrthemes',
             'ggrepel','robustbase')

inst.load.pkg <- function(pkg){ 
  if (!require(pkg, character.only = TRUE)) {
      install.packages(pkg, dependencies = TRUE)
      library(pkg, character.only = TRUE)
  }
}

invisible(lapply(pkgs2use,inst.load.pkg))
rm(pkgs2use,inst.load.pkg)
```

```{r message=FALSE}
HCdat <- read_csv(here('Data','HCdata.csv'),col_types="TiiD??fffffifffddddddiiii")
#HCdat$QTime <- as.yearqtr(HCdat$QTime, format = "%Y-%q")
HCdat$QTime <- yearquarter(HCdat$QTime)
HCdat$QTime <- yearquarter(HCdat$QTime)

TypeVars <- as.character(unique(HCdat$TypeOff))
RegionVars <- as.character(unique(HCdat$Region))
Periods <- c('Daily','Weekly','Monthly','Quarterly') 
Events <- c('Brexit','First Lockdown','Second Lockdown','Third Lockdown')
Years <- c('2011','2021','Change 2011-21')
TypeDivers <- c('Ethnicity','Religiosity')
triggerDates <- as_date(c('2020-01-20','2020-03-26','2020-11-05','2021-01-04'))
```

Global Hate Crimes {data-icon="fa-signal"}
=======================================================================

Column {.sidebar data-height=150}
-----------------------------------------------------------------------

```{r}
radioButtons("response", "Select Response", choices = c('Counts','Cambridge Hate Crime Index'))
selectInput("period",label='Select a Periodicity', choices = c(Periods),selected='Daily',width='200px')
selectInput("tipo_crim",label='Select a Crime Type', choices = c('ALL',TypeVars),selected='ALL',width='200px')
#selectInput("trigger",label='Select an Event', choices = c('None',Events),selected='None',width='200px')
checkboxGroupInput("trigger", label = "Select an Event",choices=Events,width='150px', inline = FALSE)
```


Column {data-width=950}
-----------------------------------------------------------------------

### Global Time Series for `r reactive(ifelse(input$tipo_crim=='ALL','All Racially or Religiously Crimes',paste('Racially or Religiously',input$tipo_crim)))`

```{r}

renderPlot({
  response <- c('CountOff','CCHI Score')[c('Counts','Cambridge Hate Crime Index') %in% input$response]
  HCdat.s <- HCdat |> 
  group_by(Time,TypeOff) |> 
  summarise(across(all_of(response), ~sum(.,na.rm = TRUE)),.groups="drop") |> 
  select(Time,TypeOff,all_of(response))
  
  if(input$period=='Weekly'){
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=yearweek(Time))} else if(input$period=='Monthly'){
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=yearmonth(Time))} else if(input$period=='Quarterly'){
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=yearquarter(Time))    
  } else{
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=Time)    
  }
  HCdat.s <- HCdat.s |> 
  group_by(NewTime,TypeOff) |> 
  summarise(across(all_of(response), ~sum(.,na.rm=TRUE)),.groups="drop") |> 
  select(NewTime,TypeOff,all_of(response))
  HCdat.s <- HCdat.s|> 
  as_tsibble(key=TypeOff,index=NewTime)
  df <- HCdat.s[str_detect(HCdat.s$TypeOff,if_else(input$tipo_crim=="ALL",".*.",input$tipo_crim)),]#HCdat.s |> 
  colnames(df)[3] <- 'response'
  #filter(str_detect(TypeOff,if_else(input$tipo_crim=="ALL",".*.",input$tipo_crim)))
  if(input$tipo_crim!='ALL'){
  fit_trends <- df |> 
  model(
    piecewise = TSLM(response ~ trend(knots = triggerDates[Events %in% input$trigger]))
  )
fc_trends <- fit_trends |>  forecast(h = 10)}

  df |> autoplot(response,alpha=0.7) +
    geom_vline(xintercept = triggerDates[Events %in% input$trigger],
             linetype = "dashed",
             lwd = 1.25,
             color = "#FF0000") +
    annotate(geom = "text",
             label = Events[Events %in% input$trigger],
             x = triggerDates[Events %in% input$trigger],
             y=20,
             col="#FF0000",
             size=3.5,
             angle = 90, 
             vjust = 1.3) +
    scale_y_continuous(limits=c(0,NA)) +
    ylab(input$response) +
    xlab(ifelse(input$period=='Weekly','Week',ifelse(input$period=='Monthly','Month',
                ifelse(input$period=='Quarterly','Quarter','Day')))) +
    theme_ipsum(axis_title_size = 12) +
    scale_fill_ipsum() +
    theme(legend.position='bottom',legend.text=element_text(size=10),legend.margin = margin()) +
    guides(color=guide_legend(nrow=2,byrow=TRUE,title='Crime Type')) +
    if(input$tipo_crim!='ALL'){geom_line(data = fitted(fit_trends),
            aes(y = .fitted),col="#FF0000",lwd=.8)}
})

```

Hate Crimes By Regions {data-icon="fa-signal"}
=======================================================================

Column {.sidebar data-height=150}
-----------------------------------------------------------------------

```{r}
radioButtons("responseR", "Select Response", choices = c('Counts','Cambridge Hate Crime Index'))
selectInput("region",label='Select a Region', choices = c(RegionVars),selected=RegionVars[1],width='200px')
selectInput("periodR",label='Select a Periodicity', choices = c(Periods),selected='Daily',width='200px')
selectInput("tipo_crimR",label='Select a Crime Type', choices = c('ALL',TypeVars),selected='ALL',width='200px')
#selectInput("trigger",label='Select an Event', choices = c('None',Events),selected='None',width='200px')
checkboxGroupInput("triggerR", label = "Select an Event",choices=Events,width='150px', inline = FALSE)
```


Column {data-width=950}
-----------------------------------------------------------------------

### Time Series for `r reactive(ifelse(input$tipo_crimR=='ALL','All Racially or Religiously Crimes',paste('Racially or Religiously',input$tipo_crimR)))` in `r reactive(input$region)`

```{r}

renderPlot({
  response <- c('CountOff','CCHI Score')[c('Counts','Cambridge Hate Crime Index') %in% input$responseR]
  HCdat.s <- HCdat  |>  filter(HCdat$Region == input$region) |> 
  group_by(Time,TypeOff) |> 
  summarise(across(all_of(response), ~sum(.,na.rm = TRUE)),.groups="drop") |> 
  select(Time,TypeOff,all_of(response))
  
  if(input$periodR=='Weekly'){
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=yearweek(Time))} else if(input$periodR=='Monthly'){
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=yearmonth(Time))} else if(input$periodR=='Quarterly'){
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=yearquarter(Time))    
  } else{
    HCdat.s <- HCdat.s |> 
      mutate(NewTime=Time)    
  }
  HCdat.s <- HCdat.s |> 
  group_by(NewTime,TypeOff) |> 
  summarise(across(all_of(response), ~sum(.,na.rm=TRUE)),.groups="drop") |> 
  select(NewTime,TypeOff,all_of(response))
  HCdat.s <- HCdat.s|> 
  as_tsibble(key=TypeOff,index=NewTime)
  df <- HCdat.s[str_detect(HCdat.s$TypeOff,if_else(input$tipo_crimR=="ALL",".*.",input$tipo_crimR)),]#HCdat.s |> 
  colnames(df)[3] <- 'response'
  #filter(str_detect(TypeOff,if_else(input$tipo_crim=="ALL",".*.",input$tipo_crim)))
  if(input$tipo_crimR!='ALL'){
  fit_trends <- df |> 
  model(
    piecewise = TSLM(response ~ trend(knots = triggerDates[Events %in% input$triggerR]))
  )
fc_trends <- fit_trends |>  forecast(h = 10)}

  df |> autoplot(response,alpha=0.7) +
    geom_vline(xintercept = triggerDates[Events %in% input$triggerR],
             linetype = "dashed",
             lwd = 1.25,
             color = "#FF0000") +
    annotate(geom = "text",
             label = Events[Events %in% input$triggerR],
             x = triggerDates[Events %in% input$triggerR],
             y=20,
             col="#FF0000",
             size=3.5,
             angle = 90, 
             vjust = 1.3) +
    scale_y_continuous(limits=c(0,NA)) +
    ylab(input$responseR) +
    xlab(ifelse(input$periodR=='Weekly','Week',ifelse(input$periodR=='Monthly','Month',
                ifelse(input$periodR=='Quarterly','Quarter','Day')))) +
    theme_ipsum(axis_title_size = 12) +
    scale_fill_ipsum() +
    theme(legend.position='bottom',legend.text=element_text(size=10),legend.margin = margin()) +
    guides(color=guide_legend(nrow=2,byrow=TRUE,title='Crime Type')) +
    if(input$tipo_crimR!='ALL'){geom_line(data = fitted(fit_trends),
            aes(y = .fitted),col="#FF0000",lwd=.8)}
})

```

Global Diversity {data-icon="fa-signal"}
=======================================================================

Column {.sidebar data-height=150}
-----------------------------------------------------------------------

```{r}
selectInput("yearG",label='Select a Year', choices = c(Years),selected=Years[1],width='200px')
selectInput("tipo_divG",label='Select Diversity Type', choices = c(TypeDivers),selected=TypeDivers[1],width='200px')
```


Column {data-width=950}
-----------------------------------------------------------------------

### Diversity (`r reactive(ifelse(input$yearG=='Change 2011-21','Change 2011-2021',ifelse(input$yearG=='2011','year 2011','year 2021')))`) in `r reactive(input$tipo_divG)`

```{r}
renderPlot({
pattern <- paste0(c('','','Change\\b.*')[c('2011','2021','Change 2011-21') %in% input$yearG] ,c('eth','relig')[c('Ethnicity','Religiosity') %in% input$tipo_divG],c('2011','2021','')[c('2011','2021','Change 2011-21') %in% input$yearG])

var2select <- colnames(HCdat)[str_detect(colnames(HCdat),pattern)]

df <- HCdat |> group_by(Region) |>
  select(all_of(c('Region',var2select))) |>
  distinct_all() |>
  set_names(c('Region','Diversity'))

ggplot(data = df, mapping = aes(x = reorder(Region, Diversity), Diversity)) + 
  geom_bar(stat = "identity",fill='blue') + coord_flip() +
  xlab('Regions') +
  geom_hline(yintercept = mean(df$Diversity),
             linetype = "dashed",
             lwd = 1.25,
             color = "#FF0000") +
  ylim(c(0,1)) +
  theme_ipsum(axis_title_size = 12) +
  scale_fill_ipsum()
})
```


Hate Crimes & Diversity {data-icon="fa-signal"}
=======================================================================


Column {.sidebar data-height=150}
-----------------------------------------------------------------------

```{r}
radioButtons("responseD", "Select Response", choices = c('Counts','Cambridge Hate Crime Index'))
selectInput("tipo_crimD",label='Select a Crime Type', choices = c('ALL',TypeVars),selected='ALL',width='200px')
selectInput("year",label='Select a Year', choices = c(Years),selected=Years[1],width='200px')
selectInput("tipo_div",label='Select Diversity Type', choices = c(TypeDivers),selected=TypeDivers[1],width='200px')
```

Column {data-width=950}
-----------------------------------------------------------------------


### Relationship between Linear Change (2015-2022) in `r reactive(ifelse(input$tipo_crimD=='ALL','All Racially or Religiously Crimes',paste('Racially or Religiously',input$tipo_crimD)))` and `r reactive(ifelse(input$year=='Change 2011-21','Change in Diversity 2011-2021',ifelse(input$year=='2011','Diversity (2011)','Diversity (2021)')))` in `r reactive(input$tipo_div)`


```{r}
trend_model <- function(df){
  lm(Response~Time,data=df)
}
mycoeff <- function(mod){
  coefficients(mod)[2]
}

myrlm <- function(..., weights = NULL) {
   lmrob(...)
}

renderPlot({
pattern <- paste0(c('','','Change\\b.*')[c('2011','2021','Change 2011-21') %in% input$year] ,c('eth','relig')[c('Ethnicity','Religiosity') %in% input$tipo_div],c('2011','2021','')[c('2011','2021','Change 2011-21') %in% input$year])

df <- HCdat[str_detect(HCdat$TypeOff,if_else(input$tipo_crimD=="ALL",".*.",input$tipo_crimD)),]
var2select <- colnames(df)[str_detect(colnames(df),pattern)]

response <- c('CountOff','CCHI Score')[c('Counts','Cambridge Hate Crime Index') %in% input$responseD]

df <- df |> group_by(Region) |>
  select(all_of(c('Region',var2select))) |>
  distinct_all() |> 
  left_join(df |> 
  select(all_of(c('Region',response,'Time'))) |> 
  group_by(Region) |> set_names(c('Region','Response','Time')) |> 
  nest() |> 
  mutate(model = purrr::map(data, trend_model)) |> 
  mutate(slopes = purrr::map(model, mycoeff)) |> 
  unnest(slopes) |> select(all_of(c('Region','slopes')))) |>
  set_names(c('Region','Diversity','Response'))

df |> ggplot(aes(x=Diversity,y=Response))+
  geom_point(pch=16,color=I('red'),size=4) +
  geom_smooth(method='lmrob',se=FALSE) +
    scale_y_continuous(limits=c(NA,NA)) +
    ylab(paste('Change Magnitude in ',input$responseD)) +
    xlab(paste('Diversity in',input$tipo_div)) +
  geom_text_repel(
    aes(label = Region),
    family = "Poppins",
    size = 4,
    min.segment.length = 0, 
    seed = 42, 
    box.padding = 0.5,
    color = "grey50"
  ) +
  labs(subtitle=paste('R-squared=',round(summary(lmrob(Response~Diversity,data=df))$r.squared,3))) +
    theme_ipsum(axis_title_size = 12) +
    scale_fill_ipsum()
})
```

About this study {data-icon="fa-globe"}
===========================================

Inputs {.sidebar data-height=400}
-----------------------------------------------------------------------
